\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-05-05 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.fls 	modified:   manuscript/main.log 	modified:   manuscript/main.out 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex 	new file:   plotting/same_distribution.ipynb

\date{ \vspace*{0.5cm} (Research In Progress)}

@@

% Police brutality, law enforcement, and crime: Evidence from Chicago
\begin{abstract}
    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, in the context of online platform development. By analyzing micro-level transactions of second homes in ten major Chinese cities from 2016 to 2022, the study explores how the strategic clustering of offline stores enhances Lianjia's influence in local communities and facilitates the creation of an extensive franchise network. This study first conducts a regression discontinuity (RD) design to quantify the optimal influence radius of these stores on housing transactions. By incorporating the optimal influence radius, this study examines the exogenous shock of Lianjia's market entry to identify a significant increase in transaction revenues. However, this effect is diminished during Covid-19 periods. In addition, the paper examines the impact of Lianjia's ACN strategy on its platformization efforts and concludes that the effect is not only from the larger client base brought by the platform, but also from the information control by sharing information within the platform. This study provides valuable insights into the synergy between offline store expansion and online platform development, highlighting their importance in the evolving real estate brokerage market.
  \end{abstract}

@@

In the real estate market, transaction costs are a critical factor for both buyers and sellers. Minimizing these costs has made the selection of competent real estate agencies a significant priority for both parties. Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communication channel between buyers and sellers \citep{glaeser_real_2017}. In addition, technological advancements coupled with the proliferation of dominant platforms have created a trend toward greater monopolization within the real estate brokerage industry, rather than fostering a competitive environment. Therefore, it is imperative to analytically examine the expansion strategies of Chinese real estate agencies, especially in the context of escalating platform-based monopolization.

@@

\citet{Rosen_hedonic} proposed a hedonic pricing model and explained the price is determined by internal and external factors affecting it. But the hedonic pricing model suffers under conditions of market asymmetry and information inequality. The seminal work on the impact of asymmetric information in markets is \citep{Akerlof_1970}, which demonstrated that markets for used cars tend to be dominated by low-quality goods, or 'lemons,' leading to market inefficiencies.  Furthermore, \citet{grossman_impossibility_1980} further argued that information effective market assumption is hard to hold in reality. Therefore,

@@

% \section{Theoretical Model}

@@

The second hand housing transaction data was collected form \href{https://bj.lianjia.com/}{lianjia.com} for ten cities ranging from 2016 to 2022. Initially, we filtered out transaction records exhibiting unusually high prices, identifying them as outliers that could skew the analysis. This was followed by the removal of records with missing values to maintain the integrity of our dataset. Furthermore, we removed all the records that are . We finally have a data with length 1,716,579 second-hand house.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} Since most of lianjia's offline stores are centered around communities, and most of our information is accurate at the community level, and to make our panel compatible, we decided to aggregate the information at the community level. By taking the average of all transaction information, we constructed the panel data with seven years.

To gather more information, we first extracted the POI data from the AutoNavi map using the web-scrawling Python program.\footnote{AutoNavi, a leading mapping application in China with a huge user base of more than 700 million, stands out for its detailed and accurate POI data and precise public transportation information. These features underscore AutoNavi's formidable lead in the digital mapping sector, highlighting its ability to provide unparalleled navigation accuracy and comprehensive urban mobility solutions. Our extracted AutoNavi map contains more than 1 million POIs for each city in each year.} We then classified the extracted POIs into different categories, the specifics of which are discussed in detail in Table \ref{tab:statistical}. This categorization was crucial for understanding the urban infrastructure and amenities available in the vicinity of the analyzed properties. We prioritized POIs within a 500-meter radius-a distance typically covered within a ten-minute walk, consistent with urban planning standards for accessible urban design. This radius was specifically chosen to reflect the immediate urban environment that influences residential desirability and value, as the majority of these POIs provide recreational services. Furthermore, some geo-informational data was also integrated into our research data, which consists of the annual gdp obtained from \citep{zhao_forecasting_2017}, nighttime lights data, obtained from \citep{elvidge_annual_2021} and air pollution data from \citep{doi:10.1021/acs.est.1c05309}. By merging these data with our research panel, we finally get the data.

To We divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the community. We can see that for income, house tour number and the are all significantly different in those communities with or without lianjia. Furthermore, we find that the those with lianjia have a

>>>>

\date{ \vspace*{0.5cm} \today}

@@

% Police brutality, law enforcement, and crime: Evidence from Chicago
\begin{abstract}
    \noindent This study examines the impact of offline store expansion by Lianjia, China's leading real estate brokerage, in the context of online platform development. By analyzing micro-level transactions of second-hand houses in ten major Chinese cities from 2016 to 2022, the study explores how the strategic clustering of offline stores enhances Lianjia's influence in local communities and facilitates the creation of an extensive franchise network. This study first conducts a regression discontinuity (RD) design to quantify the optimal influence radius of these stores on housing transactions. By incorporating the optimal influence radius, this study examines the exogenous shock of Lianjia's market entry to identify a significant increase in transaction revenues. However, this effect is diminished during Covid-19 periods. In addition, the paper examines the impact of Lianjia's ACN strategy on its platformization efforts and concludes that the effect is not only from the larger client base brought by the platform, but also from the information control by sharing information within the platform. This study provides valuable insights into the synergy between offline store expansion and online platform development, highlighting their importance in the evolving real estate brokerage market.
  \end{abstract}

@@

In the real estate market, transaction cost is a critical factor for both buyers and sellers. Minimizing these costs has made the selection of competent real estate agencies a significant priority for both parties. Especially in the context of China's burgeoning real estate market, brokerage firms are assuming an increasingly important role in facilitating the communication channel between buyers and sellers \citep{glaeser_real_2017}. In addition, technological advancements coupled with the proliferation of dominant platforms have created a trend toward greater monopolization within the real estate brokerage industry, rather than fostering a competitive environment. Therefore, it is imperative to analytically examine the expansion strategies of Chinese real estate agencies, especially in the context of escalating platform-based monopolization.

@@

\citet{Rosen_hedonic} proposed a hedonic pricing model and explained the price is determined by internal and external factors affecting it. But the hedonic pricing model suffers under conditions of market asymmetry and information inequality. The seminal work on the impact of asymmetric information in markets is \citep{Akerlof_1970}, which demonstrated that markets for used cars tend to be dominated by low-quality goods, or 'lemons,' leading to market inefficiencies.  Furthermore, \citet{grossman_impossibility_1980} further argued that information effective market assumption is hard to hold in reality. Therefore, the real estate market, which is characterized by information asymmetry, is particularly vulnerable to the adverse selection problem. In this context, the role of real estate brokerages is crucial, as they act as intermediaries between buyers and sellers, providing valuable information and facilitating transactions.

@@

\section{Theoretical Model}

To characterize the real estate brokerage market, we can assume that there are two types of brokerages in the market, where the type $1$ denote the large real estate brokerage that is incorporating the online platform and the offline stores strategies, and the type $2$ denote the small real estate brokerage that only have the offline stores and they should compete with the type $1$ stores and type $2$ stores in the market.

We can assume that there are $N$ number of communities in the market, and each market has $\kappa_i, i \in \{1, \ldots, N\}$ number of houses listed. The houses listed follows a AR(1) model specified by:

\begin{equation}
  \kappa_{i, t} = \rho_{i} \kappa_{i-1, t} + \epsilon_{i, t}, \label{eq:ar1}
\end{equation}

where $\rho_i$ is the parameter and $\varepsilon_{i, t} \sim \mathcal{N}(0, \sigma_{i, t}^2)$. We can assume that the price of the house is determined by the hedonic pricing model, and without loss of generality, the price follows a standard uniform distribution, $P_i \sim Uniform[0, 1]$.

The number of two types of brokerages are characterized by $B_{1, i}$ and $B_{2, i}$, respectively. The brokerages have the same positive cost function denoted as $C(\cdot)$ where $\frac{\partial C(\cdot)}{\partial B_{1, t}} > 0$ and $\frac{\partial C^2(\cdot)}{\partial B_{1, t}^2} > 0$. The intuition is that because of the marginal cost of the platform is $0$, when considering the cost of opening additional stores in the market, the brokerage does not incur that cost into consideration and therefore, the cost function is equal for both types of stores. Moreover, the marginal cost of opening additional stores is increasing, which is consistent with the real estate brokerage market.

There are $L$ number of customers that arrive in the market at random poission rate $\lambda$ and for current issue, we can first assume that the customers are indifferent when selecting the brokerages and we can release this assumption later to make the customers have private preference towards each type of brokerages. The probability of selecting the brokerage $i$ is given by:

\begin{equation}
  p_i = \frac{B_{i, t}}{B_{1, t} + B_{2, t}}. \label{eq:prob}
\end{equation}

The profit of the brokerage in the community is given by $\pi_1(p_1, p_2) = $

give me a mathematical economics model characterizing the partial equilibrium of real estate broekrage and the competitive market where there are two types of brokerages denoted 1 if the brokerage is the large brokerage that it can communicate with other stores in different regions of the same type 1 brokerage, and denote 2 if it is small brokerage that it can not communicate with the other brokerages in the market

In the later, we can also assume that people have private information or preference towards different brokerages so that there will be another proposition demonstrated about the model.

We can examine the following two effects:

\begin{itemize}
  \item The real estate brokerage's network effect where the brokerages are more likely to form a edge between each other (this is demonstrated in the ACN's brokerage network model)
  \item The partial effect of the network effect is not characterized by the price level changes or the brokerage fee increase.
  \item The network effect should be demonstrated by the increase in the number of transactions and the number of the stores within given radius comparing with the total number of houses in this market.
\end{itemize}

@@

The second hand housing transaction data was collected form \href{https://bj.lianjia.com/}{lianjia.com} for ten cities ranging from 2016 to 2022. Initially, we filtered out transaction records exhibiting unusually high prices, identifying them as outliers that could skew the analysis. We then removed records with missing values to maintain the integrity of our dataset. We also removed any records that were listed duplicated. We finally have a data with length 1,716,579 second-hand house.\footnote{Due to government restrictions, four of these cities did not list the transaction price for each transaction during the study period.} Since most of the offline stores in lianjia are community-based, and most of the information is accurate at the community level, we decided to aggregate the information at the community level to make our panel compatible. By taking the average of all transaction information, we constructed the panel data with seven years.

To gather other characteristics information, we first extracted the POI data from the AutoNavi map using the web-scrawling Python program.\footnote{AutoNavi, a leading mapping application in China with a huge user base of more than 700 million, stands out for its detailed and accurate POI data and precise public transportation information. These features underscore AutoNavi's formidable lead in the digital mapping sector, highlighting its ability to provide unparalleled navigation accuracy and comprehensive urban mobility solutions. Our extracted AutoNavi map contains more than 1 million POIs for each city in each year.} We then classified the extracted POIs into different categories, the specifics of which are discussed in detail in Table \ref{tab:statistical}. This categorization was crucial for understanding the urban infrastructure and amenities available in the vicinity of the analyzed properties. We prioritized POIs within a 500-meter radius-a distance typically covered within a ten-minute walk, consistent with urban planning standards for accessible urban design. This radius was specifically chosen to reflect the immediate urban environment that influences residential desirability and value, as the majority of these POIs provide recreational services. Furthermore, some geo-informational data was also integrated into our research data, which consists of the annual gdp obtained from \citep{zhao_forecasting_2017}, nighttime lights data, obtained from \citep{elvidge_annual_2021} and air pollution data from \citep{doi:10.1021/acs.est.1c05309}. By merging these data with our research panel, we finally get the data.

To check the robustness of the data, we divide our data to those with lianjia and those without lianjia and to check whether lianjia's offline stores have influential effect on the transaction effect in the community. We can see that for income, house tour number and the are all significantly different in those communities with or without lianjia. Furthermore, we find that the other brokerages are also have the same tendency that they typically

This figure is shown in Figure \ref{fig:same_distribution}
